Can Cultural Transmission Explain The Evolution of Cooperative Behavior?

### 2020-05-01 ms/main.tex

In this case eq.~\ref{eq:horizontal} becomes $\hat{p}=p$ and eq.~\ref{eq:nextgen_parents} becomes:
\begin{equation} 
\begin{split}\label{eq:nextgen_parents_oblique_only}
p' 
& = p^2 (1 - (1-p) (1-\alpha) T_B) \\
& + p(1-p)(p (1-\alpha) + \alpha) T_A \\
& + p(1-p)((1-\alpha)T_B + (1-\alpha)(p+(1-p)(1-T_B))) \\
& + (1-p)^2 p (1-\alpha) T_A
\end{split}
\end{equation}

\textbf{Result 2: Oblique and horizontal transmission of cooperation.} The frequency of phenotype $A$ among adults increases if $p'>p$.
From eq.~\ref{eq:nextgen_parents_oblique_only}, this occurs when:
\begin{equation} \label{eq:oblique_only_result}
T_A>T_B. 
\end{equation}
% TODO proof.

>>>>

In this case eq.~\ref{eq:horizontal} becomes $\hat{p}=p$ and eq.~\ref{eq:nextgen_parents_simplified} becomes:
\begin{equation} 
\begin{split}\label{eq:nextgen_parents_oblique_only}
p' = p^2\cdot(T_B-T_A) + p\cdot(1+T_A-T_B)
\end{split}
\end{equation}

\textbf{Result 2: Oblique and horizontal transmission of cooperation.} The frequency of phenotype $A$ among adults increases if $p'>p$.
From eq.~\ref{eq:nextgen_parents_oblique_only}, this occurs when:
\begin{equation} \label{eq:oblique_only_result}
T_A>T_B. 
\end{equation}
